### 2021-01-31 博士/毕业论文/ucasthesis/Tex/Chap_end.tex
删除 vspace 对行距的压缩
完善 end 一章图片尺寸

\begin{figure}[t]
    \centering
    \includegraphics[width=0.48\textwidth]{Img/end/visulization.pdf}
    \vspace{-0.8cm}
    \caption{A comparison of our method with SiamMask and SiamFCv2. The example frames are from the GOT-10k testing set. Our approach effectively handles poor object appearance compared to existing approaches.}
    \vspace{-0.5cm}
    \label{fig:visulization}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{Img/end/net_v3.pdf}
    \vspace{-0.5cm}
    \caption{
    Overview of our two-stage SiamTFA.
    %At the first stage, a siamese FPN equipped with a temporal aggregation module provides features of the template image and the search image. Then the feature modulation module is used to merge the features and generate proposals.
    %proposals of the object given in the first-frame bounding box. 
    %At the second stage, 
    The proposal generation stage aims to generate proposals that are visually similar to the given template target. The refine stage aims to select the target from candidate proposals.}
    \label{fig:SiamTFA}
\end{figure*}

@@

\section{Experiments}
In this section, we first present the implementation details.
Then we evaluate out method on GOT-10K \cite{Huang_2019} testing set and the UAV20L \cite{mueller2016benchmark} dataset.
\vspace{-2mm}
\subsection{ Implementation details}
The proposed network is trained on the training set of GOT-10k \cite{Huang_2019} and the backbone is pretrained on ImageNet.
We apply stochastic gradient descent with momentum of 0.9 and set the weight decay to 0.0005.
The learning rate is decreased from $10^{-2}$ to $10^{-4}$.
The batch size is set to 2 and the network is trained for 90000 iterations.
Our tracker is implemented in Python, using PyTorch.
%First stage, we select 4000 proposals to send to stage2, the positive/negative rate is 1:3.
%To shift channels $K=2$.
%Because of the memory limit, the batch size is 2.
%To calculate the loss, $\lambda = 1$.
%For both training and testing, the size of a template image is 
% 其实有些对不上。按论文上讲，第一阶段是找到若干候选框。第二阶段是得到唯一结果。实际上是，第一阶段得到若干候选框，第二阶段进一步筛选得到约10个候选框（这才是真正的相似目标），然后按IoU和得分来选择最终结果。
% For test, we select top 100 proposals to send to stage2. The we use NMS to select top 10 object. 
\vspace{-2mm}
\subsection{Evaluation on GOT-10k dataset}

\iffalse
\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{images/success_plot.png}
    \vspace{-5mm}
    \caption{Overall performance on GOT-10k, ranked by their average overlap (AO) scores.}
    \label{fig:got10k}
     \vspace{-3mm}
\end{figure}
\fi
\begin{table}
\centering
\caption{Performance of our algorithm with different components on GOT-10k test set.}
\begin{tabular}{c c c c c}
\bottomrule
\begin{tabular}[x]{@{}c@{}}Temporal\\aggregation\end{tabular} & \begin{tabular}[x]{@{}c@{}}Adversarial\\dropout\end{tabular} & $AO$ & $SR_{0.50}$ & $SR_{0.75}$ \\ 
\hline
          &           & 0.542 & 0.607 & 0.456 \\
\checkmark&           & 0.561 & 0.645 & 0.480 \\
\checkmark&\checkmark & 0.577 & 0.662 & 0.509 \\
\bottomrule
\label{tabel:ablation}
\end{tabular}
\vspace{-0.8cm}
\end{table}
\begin{table}
\centering
\caption{Comparing the results of our approach against other approaches over the GOT-10k test set.}
\begin{tabular}{l l l l}
\bottomrule
Method   &  $AO$   &  $SR_{0.50}$ & $SR_{0.75}$  \\
\hline
Ours &  $\textbf{0.577}^\textbf{1}$ & $\textbf{0.662}^\textbf{1}$  & $\textbf{0.509}^\textbf{1}$  \\
SiamMask &  0.459&  0.560 &0.205 \\
SiamFCv2 &  0.374&  0.404 &0.144 \\
SiamFC   &  0.348&  0.353 &0.098 \\
GOTURN	 &  0.347&  0.375 &0.124 \\
CCOT	 &  0.325&  0.328 &0.107 \\
ECO	     &  0.316&  0.309 &0.111 \\
CF2	     &  0.315&  0.297 &0.088 \\
MDNet	 &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}
In this subsection, we evaluate our method on GOT-10k \cite{Huang_2019} dataset.
% Say something about this dataset.
GOT-10k is a recent large-scale high-diversity dataset consisting of over 10,000 video sequences with targets annotated by axis-aligned bounding boxes. 
%Note that the classes between training and test sets are zero-overlapped. 
%This one-shot protocol avoids the evaluation bias towards familiar objects. 
The GOT-10k testing set includes 180 sequences with 84 different object classes and 32 motion patterns. As performance measure, we use the average overlap (AO) scores and success rate (SR) as proposed in \cite{Huang_2019}. The AO denotes the average of overlaps between all groundtruth and estimated bounding boxes, while the SR measures the percentage of successfully tracked frames where the overlaps exceed 0.5/0.75.

@@

\begin{figure}[t]
\begin{minipage}[b]{.48\linewidth}
  \centering
  \centerline{\includegraphics[width=5.0cm]{Img/end/quality_plot_overlap_OPE_AUC.png}}
\end{minipage}
\hfill
\begin{minipage}[b]{0.48\linewidth}
  \centering
  \centerline{\includegraphics[width=5.0cm]{Img/end/quality_plot_error_OPE_threshold.png}}
\end{minipage}
\vspace{-5mm}
%
\caption{Success and precision plots on UAV20L dataset.}
\vspace{-3mm}
\label{fig:uav20l}
%
\end{figure}
\vspace{-2mm}
\subsection{Evaluation on UAV20L dataset}
In this subsection, we evaluate our tracker on the UAV20L \cite{mueller2016benchmark} long term tracking dataset.
% say something about this dataset: length, 20段
It contains 20 HD video sequences captured from a low-altitude aerial perspective with average sequence length of 2934 frames.
% It has mean frames of 2934 and max frames of 5527.
% say something about the measures. 
In this experiment, all trackers are compared using two measures: precision and success. Precision is measured as the distance between the centers of the predicted bounding box and the corresponding ground truth bounding box. Success is measured as the intersection over union of pixels in predicted bounding box and those in ground truth bounding box.
% say something about the accuracy.
In Fig. \ref{fig:uav20l}, we can find that the proposed algorithm achieves better tracking performance compared with some representative trackers.
In the success plot, our tracker obtains an AUC score of 0.606.
% PTAV is ... Compared with it, our is higher. This demonstrates the effectiveness of our designed architecture.
In the precision plot, the proposed algorithm obtains a score of 0.804.
% MUSTER is ... Compared with it, our is higher.
It shows that our tracker surpass other state-of-the-art algorithms, such as SiamRPN \cite{li2018high} and PTAV \cite{fan2017parallel}. This demonstrates the effectiveness of our tracker in long-term tracking scenario. 
%designed architecture.
%It shows that our tracker surpass another siamese tracker -- SiamRPN. This demonstrates the effectiveness of our designed architecture. Moreover, compared with other state-of-the-art algorithms, such as PTAV \cite{} and MUSTER \cite{}, our trackers are still superior in terms of precision.
\section{Conclusion}
%一句话指出我们提出了什么。
In this paper, we introduce a novel siamese architecture for visual object tracking.
Specifically, our proposed algorithm contains two main modules, \textit{i.e.} temporal aggregation module and adversarial dropout module. The temporal aggregation module improves  the per-frame features by aggregating features of adjacent frames. The adversarial dropout module improves the discrimination power of the siamese tracking network.
%say something about the experiment.
Extensive experimental results show that the proposed algorithm performs favorably against the state-of-the-art algorithms.

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/end/visulization.pdf}
    \caption{A comparison of our method with SiamMask and SiamFCv2. The example frames are from the GOT-10k testing set. Our approach effectively handles poor object appearance compared to existing approaches.}
    \label{fig:visulization}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \includegraphics[width=1.0\textwidth]{Img/end/net_v3.pdf}
    \caption{
    Overview of our two-stage SiamTFA.
    %At the first stage, a siamese FPN equipped with a temporal aggregation module provides features of the template image and the search image. Then the feature modulation module is used to merge the features and generate proposals.
    %proposals of the object given in the first-frame bounding box. 
    %At the second stage, 
    The proposal generation stage aims to generate proposals that are visually similar to the given template target. The refine stage aims to select the target from candidate proposals.}
    \label{fig:SiamTFA}
\end{figure*}

@@

\section{Experiments}
In this section, we first present the implementation details.
Then we evaluate out method on GOT-10K \cite{Huang_2019} testing set and the UAV20L \cite{mueller2016benchmark} dataset.
\subsection{ Implementation details}
The proposed network is trained on the training set of GOT-10k \cite{Huang_2019} and the backbone is pretrained on ImageNet.
We apply stochastic gradient descent with momentum of 0.9 and set the weight decay to 0.0005.
The learning rate is decreased from $10^{-2}$ to $10^{-4}$.
The batch size is set to 2 and the network is trained for 90000 iterations.
Our tracker is implemented in Python, using PyTorch.
%First stage, we select 4000 proposals to send to stage2, the positive/negative rate is 1:3.
%To shift channels $K=2$.
%Because of the memory limit, the batch size is 2.
%To calculate the loss, $\lambda = 1$.
%For both training and testing, the size of a template image is 
% 其实有些对不上。按论文上讲，第一阶段是找到若干候选框。第二阶段是得到唯一结果。实际上是，第一阶段得到若干候选框，第二阶段进一步筛选得到约10个候选框（这才是真正的相似目标），然后按IoU和得分来选择最终结果。
% For test, we select top 100 proposals to send to stage2. The we use NMS to select top 10 object. 
\subsection{Evaluation on GOT-10k dataset}

\iffalse
\begin{figure}[t]
    \centering
    \includegraphics[width=0.45\textwidth]{images/success_plot.png}
    \caption{Overall performance on GOT-10k, ranked by their average overlap (AO) scores.}
    \label{fig:got10k}
\end{figure}
\fi
\begin{table}
\centering
\caption{Performance of our algorithm with different components on GOT-10k test set.}
\begin{tabular}{c c c c c}
\bottomrule
\begin{tabular}[x]{@{}c@{}}Temporal\\aggregation\end{tabular} & \begin{tabular}[x]{@{}c@{}}Adversarial\\dropout\end{tabular} & $AO$ & $SR_{0.50}$ & $SR_{0.75}$ \\ 
\hline
          &           & 0.542 & 0.607 & 0.456 \\
\checkmark&           & 0.561 & 0.645 & 0.480 \\
\checkmark&\checkmark & 0.577 & 0.662 & 0.509 \\
\bottomrule
\label{tabel:ablation}
\end{tabular}
\end{table}
\begin{table}
\centering
\caption{Comparing the results of our approach against other approaches over the GOT-10k test set.}
\begin{tabular}{l l l l}
\bottomrule
Method   &  $AO$   &  $SR_{0.50}$ & $SR_{0.75}$  \\
\hline
Ours &  $\textbf{0.577}^\textbf{1}$ & $\textbf{0.662}^\textbf{1}$  & $\textbf{0.509}^\textbf{1}$  \\
SiamMask &  0.459&  0.560 &0.205 \\
SiamFCv2 &  0.374&  0.404 &0.144 \\
SiamFC   &  0.348&  0.353 &0.098 \\
GOTURN	 &  0.347&  0.375 &0.124 \\
CCOT	 &  0.325&  0.328 &0.107 \\
ECO	     &  0.316&  0.309 &0.111 \\
CF2	     &  0.315&  0.297 &0.088 \\
MDNet	 &  0.299&  0.303 &0.099 \\
%CFNetc2	 &  0.293&  0.265 &0.087 \\
%ECOhc	 &  0.286&  0.276 &0.096 \\
\bottomrule
\end{tabular}
\label{table:got}
\end{table}
In this subsection, we evaluate our method on GOT-10k \cite{Huang_2019} dataset.
% Say something about this dataset.
GOT-10k is a recent large-scale high-diversity dataset consisting of over 10,000 video sequences with targets annotated by axis-aligned bounding boxes. 
%Note that the classes between training and test sets are zero-overlapped. 
%This one-shot protocol avoids the evaluation bias towards familiar objects. 
The GOT-10k testing set includes 180 sequences with 84 different object classes and 32 motion patterns. As performance measure, we use the average overlap (AO) scores and success rate (SR) as proposed in \cite{Huang_2019}. The AO denotes the average of overlaps between all groundtruth and estimated bounding boxes, while the SR measures the percentage of successfully tracked frames where the overlaps exceed 0.5/0.75.

@@

\begin{figure}[t]
\begin{minipage}[b]{0.5\textwidth}
  \centering
  \centerline{\includegraphics[width=1.0\textwidth]{Img/end/quality_plot_overlap_OPE_AUC.png}}
\end{minipage}
\hfill
\begin{minipage}[b]{0.5\textwidth}
  \centering
  \centerline{\includegraphics[width=1.0\textwidth]{Img/end/quality_plot_error_OPE_threshold.png}}
\end{minipage}
%
\caption{Success and precision plots on UAV20L dataset.}
\label{fig:uav20l}
%
\end{figure}
\subsection{Evaluation on UAV20L dataset}
In this subsection, we evaluate our tracker on the UAV20L \cite{mueller2016benchmark} long term tracking dataset.
% say something about this dataset: length, 20段
It contains 20 HD video sequences captured from a low-altitude aerial perspective with average sequence length of 2934 frames.
% It has mean frames of 2934 and max frames of 5527.
% say something about the measures. 
In this experiment, all trackers are compared using two measures: precision and success. Precision is measured as the distance between the centers of the predicted bounding box and the corresponding ground truth bounding box. Success is measured as the intersection over union of pixels in predicted bounding box and those in ground truth bounding box.
% say something about the accuracy.
In Fig. \ref{fig:uav20l}, we can find that the proposed algorithm achieves better tracking performance compared with some representative trackers.
In the success plot, our tracker obtains an AUC score of 0.606.
% PTAV is ... Compared with it, our is higher. This demonstrates the effectiveness of our designed architecture.
In the precision plot, the proposed algorithm obtains a score of 0.804.
% MUSTER is ... Compared with it, our is higher.
It shows that our tracker surpass other state-of-the-art algorithms, such as SiamRPN \cite{li2018high} and PTAV \cite{fan2017parallel}. This demonstrates the effectiveness of our tracker in long-term tracking scenario. 
%designed architecture.
%It shows that our tracker surpass another siamese tracker -- SiamRPN. This demonstrates the effectiveness of our designed architecture. Moreover, compared with other state-of-the-art algorithms, such as PTAV \cite{} and MUSTER \cite{}, our trackers are still superior in terms of precision.
\section{Conclusion}
%一句话指出我们提出了什么。
In this paper, we introduce a novel siamese architecture for visual object tracking.
Specifically, our proposed algorithm contains two main modules, \textit{i.e.} temporal aggregation module and adversarial dropout module. The temporal aggregation module improves  the per-frame features by aggregating features of adjacent frames. The adversarial dropout module improves the discrimination power of the siamese tracking network.
%say something about the experiment.
Extensive experimental results show that the proposed algorithm performs favorably against the state-of-the-art algorithms.
